CS182: NBA Scheduler

### 2015-10-28 proposal.tex
updates

	\begin{enumerate}
		\item Some form of greedy next-best search in choosing the next game - choose the next game for a team that makes sure this constraint is met then perform arc consistency
		\item Generate some heuristic based on the number of games left against divisional opponents (who would be geographically closer) to perform some kind of A* search
		\item Research online for other techniques that haven't been discussed in class - surprisingly this has been an issue well researched in the NFL but not the NBA (probably because that's a smaller problem with only 16 games), but perhaps we can gain some insights from reading papers optimizing their schedule
	\end{enumerate}

@@

>>>>

	\begin{enumerate}
		\item Some form of greedy next-best search in choosing the next game - choose the next game for a team that makes sure this constraint is met then perform arc consistency
		\item The minimizing distance problem is classic TSP - could try to model this problem in form of A* and find a heuristic based on number of divisional games remaining (divisional games are regionally closer)
		\item Research online for other techniques that haven't been discussed in class - surprisingly this has been an issue well researched in the NFL but not the NBA (probably because that's a smaller problem with only 16 games), but perhaps we can gain some insights from reading papers optimizing their schedule
	\end{enumerate}

@@

	\section{Resources}
	\begin{itemize}
		\item \url{http://www.public.asu.edu/~huanliu/AI04S/project1.htm}
		\item \url{http://www.cc.gatech.edu/~bdilkina/papers/NFLsched1.pdf}
		\item \url{http://www.sloansportsconference.com/wp-content/uploads/2015/02/SSAC15-RP-Finalist-Alleviating-competitive-imbalance-in-NFL-schedules.pdf}
	\end{itemize}
